%-------------------------
% Resume in Latex
% Author: Shakra Shamim
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeading}[3]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
        \small #1 & \textbf{\small #2} \\%
        \multicolumn{2}{l}{\small #3}%
    \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}

\begin{document}

%----------HEADING----------
\begin{center}
    {\Huge \scshape Rahul Kumar Bharti} \\ \vspace{4pt}
    \textbf{\Large \scshape Mern Stack Developer} \\ \vspace{4pt}
    \small \faPhone\ +91-7618805084 ~ 
    \href{mailto:rahul.kbharti2002@gmail.com}{\faEnvelope\ \underline{rahul.kbharti2002@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/rahul-kbharti}{\faLinkedin\ \underline{linkedin.com/in/rahul-kbharti}} 
    \href{https://github.com/rahulkbharti}{\faGithub\ \underline{github.com/rahulkbharti}} 
\end{center}

% %-----------SUMMARY-----------
% \section{Summary}
% Full Stack Developer skilled in building scalable, high-performance web applications using React.js, Node.js, Express.js, MongoDB, and MySQL. Experienced in implementing REST APIs, authentication (JWT, OAuth), and deploying production-ready applications.

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {B.Tech. in Information Technology}{Graduated: 2025}
    {Govt. Engineering College, Ambedkar Nagar}{CGPA: 8.0 / 10}
\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{Skills}
\textbf{Frontend:} React.js, Next.js, Redux, Tailwind CSS, Material UI, HTML5, CSS3, Responsive Design \\
\textbf{JavaScript Ecosystem:} JavaScript (ES6+), TypeScript, WebSockets \\
\textbf{Backend:} Node.js, Express.js, Mongoose ORM, REST API Development, Authentication (JWT, OAuth) \\
\textbf{Databases:} MongoDB, MySQL \\
\textbf{Tools \& Platforms:} Git, GitHub, Postman, Figma, Render \\
\textbf{Additional:} CI/CD (GitHub Actions), Docker (basic), Azure Blob Storage, Unit Testing (Jest)


%-----------INTERNSHIP-----------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {Frontend Developer Intern}{October 2023 -- December 2023}
    {Ekalsutra Edtech Pvt. Ltd., Akabarpur, Uttar Pradesh}{Tools Used: Excel, SQL, Power BI} 
    \resumeItemListStart
         \resumeItem{Developed a highly responsive, production-grade admin dashboard using React.js, Material UI, and Redux Toolkit, achieving 95\%+ design fidelity from Figma mockups.}
         \resumeItem{Boosted performance by 30\% through API integration with React Query, implementing intelligent caching to minimize re-renders.}
         \resumeItem{Built and deployed 15+ robust form workflows using Formik \& Yup, reducing validation errors by 25\% and improving user experience.}
         \resumeItem{Secured application with JWT authentication, adding protected routes and token validation for enhanced security.}
         \resumeItem{Executed 50+ API tests via Postman, ensuring high reliability and performance of integrated services.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  % Project 1 Start
  \resumeProjectHeading
      {\textbf{Real-Time Video Chat App } $|$ \emph{React.js, WebRTC, Socket.io}}{February 2025 -- March 2025}
      {Live: \href{https://real-time-video-chat.onrender.com/}{real-time-video-chat.onrender.com} $|$ 
      GitHub: \href{https://github.com/rahulkbharti/real-time-video-chat}{github.com/rahulkbharti/real-time-video-chat}} 
      \resumeItemListStart
         \resumeItem{Built an Omegle-like real-time video chat platform using WebRTC and Socket.io, enabling peer-to-peer connections.}
         \resumeItem{Developed interest-based matching with a queue system and semaphore locks, ensuring duplicate-free 1:1 pairing.}
         \resumeItem{Created custom React hooks (useWebRTC, useMedia) for efficient WebRTC setup and media handling, reducing boilerplate and improving maintainability.}    
      \resumeItemListEnd
  % Project 2 Start
   \resumeProjectHeading
      {\textbf{Library Management ERP Solution } $|$ \emph{React.js, Node.js, MySQL}}{July 2025 -- August 2025}
      {Live: \href{https://library-management-erp-solution.onrender.com/}{library-management-erp-solution.onrender.com/} $|$ GitHub: \href{https://github.com/rahulkbharti/}{github.com/rahulkbharti/}} 
      \resumeItemListStart
         \resumeItem{Engineered a full-stack ERP solution featuring a React.js + Material UI frontend and Node.js/Express backend, supporting 3 distinct user roles (Admin, Staff, Member).}
         \resumeItem{Implemented secure authentication using JWT + Google OAuth 2.0 with redux-persist for session management.}
         \resumeItem{Designed a normalized MySQL database ensuring data consistency, isolation, and security for multi-role operations.}
         \resumeItem{Developed 15+ Formik forms with Yup validation and Axios interceptors, improving data integrity and error handling.}
      \resumeItemListEnd
      
  % Project 3 Start
   \resumeProjectHeading
      {\textbf{M3U8 Video Streaming App} $|$ \emph{FFmpeg, Azure Blob Storage, MongoDB, HLS.js, Nodejs}}{March 2025 -- April 2025}
      {Live: \href{https://rahulkbharti.github.io/m3u8-video-streaming}{rahulkbharti.github.io/m3u8-video-streaming} $|$ GitHub: \href{https://github.com/rahulkbharti/}{github.com/rahulkbharti/}} 
      \resumeItemListStart
         \resumeItem{Developed a scalable adaptive video streaming service using Node.js with FFmpeg and Azure Blob Storage, enabling multi-resolution HLS streaming.}
         \resumeItem{Implemented secure dynamic M3U8 playlist generation with signed URLs and expiry tokens, backed by MongoDB for metadata.}
         \resumeItem{Designed a responsive video player using HLS.js + Plyr.js, supporting adaptive bitrate and video thumbnails.}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards \& Certifications}
\resumeItemListStart

  \resumeItem{\textbf{Top 0.5\% in TCS CodeVita – 2024:} Ranked among top 1961 out of more than 4,40,000 participants for advanced problem-solving.}

\resumeItemListEnd



\end{document}
